Creating More Meaningful Explanations for Audio Deepfake Detection

### 2025-02-13 draft.tex
change method descriptions

			clarification is in the following section. Figure \ref{fig:model_plot} depicts the
			general structure of the model, with the submodel components being connected to the
			terminus model for final processing. Figures \ref{fig:mel_model_plot} and
			\ref{fig:term_model_plot} offer a further look into the architecture, being an example
			of one submodel, specifically the submodel for the mel-spectrogram feature, as well as
			a look into a terminus model with three hidden layers respectively.

@@

					\includegraphics[width=0.4\textwidth]{images/mel_model_plot.png}
					\caption{Example of a submodel for the mel-spectrogram features, including the
					hidden layers and output sizes.}
					\label{fig:mel_model_plot}

@@

					\includegraphics[width=0.4\textwidth]{images/term_model_plot.png}
					\caption{Example of a terminus model with three hidden layers.}
					\label{fig:term_model_plot}

@@

			LIME-evaluation. Intermediate data was generated by first decomposing the surrogate
			model into its component models, the sub-models and the terminus, and for each
			sub-model, running a prediction on the given input features. The results of the
			predictions of the sub-models were stored and used for further analysis. This was done
			not only for the sample explanation data but also for the training data, to use as an
			input for the LIME explainer.

>>>>

			clarification is in the following section.
			Figure \ref{fig:model_plot} depicts the meta-structure of our hybrid model, with each
			feature first being processed in its own separate sub-model before being concatenated
			into the terminus model at the end, which produces the final result.
			Figure \ref{fig:submodel} offers a deeper look into the general architecture of a
			singular sub-model in our method. The sub-models begin with an input layer, taking
			either a vector or matrix depending on the dimensionality of the feature to which the
			model is tailored. The inputs are then passed into alternating convolutional and
			pooling layers, in order to increase the localized pattern detection capability within
			the sub-models. Figure \ref{fig:term_model} is a generalized representation of the
			terminus model, which has a classic perceptron architecture, with a varying number of
			hidden layers, depending on the experiment.

@@

					\includegraphics[width=0.4\textwidth]{images/submodel.png}
					\caption{A generalized representation of a sub-model, with the input as either
					a vector or a matrix followed by alternating convolutional and pooling layers,
					with the output as a flattened vector.}
					\label{fig:submodel}

@@

					\includegraphics[width=0.4\textwidth]{images/term_model.png}
					\caption{A generalized representation of a terminus model, which can have a
					varying amount of hidden layers.}
					\label{fig:term_model}

@@

			LIME-evaluation, the prediction outputs of the sub-models, in order to determine what
			the input of the terminus model would be. Intermediate data was generated by first
			decomposing the surrogate model into its component models, the sub-models and the
			terminus, and for each sub-model, running a prediction on the given input features.
			The results of the predictions of the sub-models were stored and used for further
			analysis. This was done not only for the sample explanation data but also for the
			training data, to use as an input for the LIME explainer.
